\documentclass{article}
\usepackage[a4paper, margin=0.5in]{geometry}
\usepackage[document]{ragged2e}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{etaremune}
\usepackage{array}
\usepackage{fixltx2e}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{textcomp}
\usepackage{xcolor}
\definecolor{links}{RGB}{11 0 128}
\hypersetup{colorlinks=true, urlcolor=links}

\begin{document}
\pagenumbering{gobble}
\begin{flushright}
Updated \today
\end{flushright}
\begin{center}
\href{https://www.linkedin.com/pub/rishabh-shah/46/962/361}{\Large \textbf{RISHABH U. SHAH}}\\\textit{Postdoctoral scientist}
\end{center}
\vspace{-2.5mm}
Office of Chief Scientist\hfill 412-807-0061 (cell)\\\href{https://www.edf.org/}{Environmental Defense Fund}
\hfill rishabhshah.92 (Skype)\\123 Mission St., 28th Floor\hfill \href{mailto:rshah6192@gmail.com}{rshah6192@gmail.com}\\San Francisco, CA 94105, USA\hfill \href{mailto:rishah@edf.org}{rishah@edf.org}
\newline
\vspace{5mm}

\hrulefill
\textit{\textbf{  Education  }}
\hrulefill
\vspace{-6mm}
\begin{center}
\begin{tabular}{p{0.17\linewidth} p{0.19\linewidth} p{0.40\linewidth} p{0.15\linewidth}}
\textbf{Degree} & \textbf{Field} & \textbf{Institution} & \textbf{Conferral}\\
\\[-2ex]
Ph.D {\small 3.6/4}\newline \begin{footnotesize}Doctor of Philosophy\end{footnotesize}
&
Mechanical \newline Engineering
&
Carnegie Mellon University {\footnotesize (CMU)}\newline \begin{footnotesize}
Pittsburgh, Pennsylvania, USA
\end{footnotesize}
&
June 2019\\[4ex]

M.S. {\small 3.88/4}\newline \begin{footnotesize}Master of Science\end{footnotesize}
&
Environmental \newline Engineering
&
University of Illinois at Urbana-Champaign \newline \begin{footnotesize}
(UIUC), Urbana, Illinois, USA
\end{footnotesize}
&
August 2015\\[4ex]

B.E. {\small 8.44/10} \newline \begin{footnotesize}Bachelor of Engineering\end{footnotesize}
&
Environmental \newline Engineering
&
Gujarat Technological University \newline \begin{footnotesize}
Ahmedabad, Gujarat, India
\end{footnotesize}
&
May 2013
\end{tabular}
\end{center}
\vspace{2mm}

\hrulefill
\textit{\textbf{  Research and work experience  }}
\hrulefill
\vspace{-4mm}
\begin{center}
\begin{tabular}{p{0.08\linewidth} p{0.875\linewidth}}
Mar '20 - now & \begin{flushleft}
\vspace{-6mm}
\textbf{High Meadows Postdoc Fellow, Atmospheric Science}
{\footnotesize \textit{\newline Office of Chief Scientist, Environmental Defense Fund}\\
Hyperlocal air pollutant mapping and analysis to improve the  effectiveness of regulatory efforts to reduce air pollution in urban areas}
\end{flushleft}
\\[-2ex]
Aug '19 - Mar '20 & \begin{flushleft}
\vspace{-6mm}
\textbf{Aerosol Mass Spectrometry Research Scientist}
{\footnotesize \textit{\newline Chemical Sciences Division, National Oceanic and Atmospheric Administration}\\
Instrument development for external calibration of aerosol mass spectrometry used for quantitative characterization of total carbon and total nitrogen content of particulate matter.}
\end{flushleft}
\\[-2ex]
July '19 & \begin{flushleft}
\vspace{-6mm}
\textbf{Postdoctoral Research Associate}
{\footnotesize \textit{\newline \vspace{-1mm} Mechanical Engineering} and \textit{Center for Atmospheric Particle Studies, CMU}}\\
Training new graduate students on the theory, unsupervised operation, calibration, maintenance, and troubleshooting of the aerosol mass spectrometer.
\end{flushleft}
\\[-2ex]
Sep '15 - June '19 & \begin{flushleft}
\vspace{-6mm}
\textbf{Graduate Research Assistant}
{\footnotesize \textit{\newline \vspace{-1mm} Mechanical Engineering} and \textit{Center for Atmospheric Particle Studies, CMU}}\\
\begin{itemize}
\item \vspace{-3mm} mobile aerosol mass spectrometry to study the spatial and temporal variability of primary and potential aerosol mass at source-specific locations.
\item \vspace{-3mm} design and characterization of an oxidation flow reactor (OFR) to simulate the atmospheric photo-oxidative formation of secondary organic aerosols from anthropogenic primary gaseous emissions.
\end{itemize}
\end{flushleft}
\\[-2ex]
Aug '16 - Dec '17 & \begin{flushleft}
\vspace{-6mm} 
\textbf{Graduate Teaching Assistant}
{\footnotesize \textit{\newline \vspace{-1mm} Course: Engineering thermodynamics, Fall 2016 and Fall 2017 semesters, Mechanical Engineering, CMU}}\\
\end{flushleft}
\\[-2ex]
May '14 -\newline Aug '15 & \begin{flushleft}
\vspace{-6mm} \textbf{Graduate Research Assistant}
{\footnotesize \textit{\newline \vspace{-1mm} Dept. of Civil and Environmental Engineering, UIUC}}\\
Laboratory experiments to characterize hygroscopic properties of emissions from biomass burning.
\end{flushleft}
\\[-2ex]
Jan -\newline May '14 & \begin{flushleft}
\vspace{-6mm} \textbf{Graduate Teaching Assistant}
{\footnotesize \textit{\newline \vspace{-1mm} Course: Environmental social science, Dept. of Natural Resources and Environmental Sciences, UIUC}}
\end{flushleft}
\end{tabular}
\end{center}
\vspace{-3mm}

\hrulefill
\textit{\textbf{  Published works (h-index = 5; total citations = 64)  }}
\hrulefill
\begin{etaremune}
\item \textbf{Shah, RU}; Coggon, MM; Gkatzelis, GI; McDonald, BC; Tasoglou, A; Huber, H; Gilman, J; Warneke, C; Robinson, AL; Presto, AA. Urban oxidation flow reactor measurements reveal significant secondary organic aerosol contributions from volatile emissions of emerging importance. \textit{Environmental Science and Technology} 2020, 54 (2), 714-725. DOI: \href{https://doi.org/10.1021/acs.est.9b06531}{10.1021/acs.est.9b06531}
\item Zimmerman, N; Li, HZ; Ellis, E; Hauryliuk, A; Robinson, ES; Gu, P; \textbf{Shah, RU}; Ye, Q; Snell, L; Subramanian, R; Robinson, AL; Apte, JS; Presto, AA. Improving Correlations between Land Use and Air Pollutant Concentrations Using Wavelet Analysis: Insights from a Low-cost Sensor Network. \textit{Aerosol and Air Quality Research} 2020, 20, 314-328. DOI: \href{http://www.aaqr.org/doi/10.4209/aaqr.2019.03.0124}{10.4209/aaqr.2019.03.0124}
\item Robinson, ES; \textbf{Shah, RU}; Messier, K; Gu, P; Li, HZ; Apte, JS; Robinson, AL; Presto, AA. Land-use regression modeling of source-resolved PM$_1$ sub-components from mobile sampling measurements. \textit{Environmental Science and Technology} 2019, 53 (15), 8925-8937. DOI: \href{https://doi.org/10.1021/acs.est.9b01897}{10.1021/acs.est.9b01897}
\item \textbf{Shah, RU.} Pre-existing and potential particulate pollution patterns in populous places: probing pollution parity for the poor and the prosperous. \href{https://search.proquest.com/openview/a52fa8ba9f1b4ffe2e6e7b09ca6e2397/1.pdf?pq-origsite=gscholar&cbl=18750&diss=y}{PhD Thesis}, Carnegie Mellon University, 2019.
\item \textbf{Shah, RU}; Robinson, ES; Gu, P; Robinson, AL; Apte, JS; Presto, AA. High-spatial-resolution mapping and source apportionment of aerosol composition in Oakland, California using mobile aerosol mass spectrometry. \textit{Atmospheric Chemistry and Physics} 2018, 18 (22), 16325-16344. DOI: \href{https://www.atmos-chem-phys.net/18/16325/2018/}{10.5194/acp-18-16325-2018}
\item Robinson, ES; Gu, P; Ye, Q; Li, HZ; \textbf{Shah, RU}; Apte, JS; Robinson, AL; Presto, AA. Restaurant Impacts on Outdoor Air Quality: Elevated Organic Aerosol Mass from Restaurant Cooking with Neighborhood-Scale Plume Extents. \textit{Environmental Science and Technology} 2018, 52 (16), 9285-9294. DOI: \href{http://pubs.acs.org/doi/10.1021/acs.est.8b02654}{10.1021/acs.est.8b02654}
\item Saha, PK; Robinson, ES; \textbf{Shah, RU}; Zimmerman, N; Apte, JS; Robinson, AL; Presto, AA. Reduced Ultrafine Particle Concentration in Urban Air: Changes in Nucleation and Anthropogenic Emissions. \textit{Environmental Science and Technology} 2018, 52 (12), 6798-6806. DOI: \href{http://pubs.acs.org/doi/10.1021/acs.est.8b00910}{10.1021/acs.est.8b00910}
\item \textbf{Shah, RU.} Hygroscopic growth and cloud condensation nuclei activity of fresh and chemically-aged biomass-pyrolyzed organic aerosol. \href{https://www.ideals.illinois.edu/handle/2142/88130}{Master's Thesis,} University of Illinois at Urbana-Champaign, 2015.
\end{etaremune}

\hrulefill
\textit{\textbf{  Manuscript(s) submitted or near submission  }}
\hrulefill
\begin{etaremune}
\item \textbf{Shah, RU}; Robinson, ES; Gu, P; Apte, JS; Marshall, JD; Robinson, AL; Presto, AA. Socio-economic disparities in exposure to urban restaurant emissions are larger than for traffic. In review, \textit{Environmental Research Letters.}
\end{etaremune}

\hrulefill
\textit{\textbf{  Research Presentations} ({\Large $\star$} = invited / funded by host)  }
\hrulefill
\begin{etaremune}
\item {\tiny TALK.} \textbf{Shah, RU}; Coggon, MM; Gkatzelis, GI; McDonald, BC; Tasoglou, A; Huber, H; Gilman, J; Warneke, C; Robinson, AL; Presto, AA. SOA Potential of Urban Volatile Chemical Product (VCP) Emissions Explored Using In-Situ Oxidation Flow Reactor. \href{http://aaarabstracts.com/2019/viewabstract.php?pid=329}{\textit{American Association for Aerosol Research Conference}}, Portland OR, 15 Oct 2019.
\item {\tiny TALK.} \textbf{Shah, RU};  Robinson, ES; Gu, P; Robinson, AL; Apte, JS; Presto, AA. Near-source spatial extents and socio-economic disparity in urban air pollution exposure. \href{http://aaarabstracts.com/2019/viewabstract.php?pid=322}{\textit{American Association for Aerosol Research Conference}}, Portland OR, 16 Oct 2019.
\item {\Large $\star$} {\tiny TALK.} \textbf{Shah, RU}. Pre-existing and potential particulate pollution patterns in populous places. \textit{Pacific Northwest National Laboratory}, Richland WA, 8 Mar 2019.
\item {\Large $\star$} {\tiny TALK.} \textbf{Shah, RU}. Pre-existing and potential particulate pollution patterns in populous places. \textit{National Oceanic and Atmospheric Administration}, Boulder CO, 7 Feb 2019.
\item {\tiny POSTER.} \textbf{Shah, RU}; Presto, AA. Potential particulates in populous and pristine places. \textit{Atmospheric Chemical Mechanisms Conference}, Davis CA, 5-8 Dec 2018.
\item {\tiny TALK.} \textbf{Shah, RU}; Robinson, ES; Gu, P; Robinson, AL; Apte, JS; Presto, AA. Mapping particulate matter in Oakland, California using mobile aerosol mass spectrometry. \href{http://aaarabstracts.com/2018IAC/viewabstract.php?pid=1032}{\textit{10\textsuperscript{th} International Aerosol Conference}}, St. Louis MO, 6 Sept 2018.
\item {\tiny TALK.} Presto, AA; Robinson, ES; \textbf{Shah, RU}; Gu, P; Li, HZ; Apte, JS; Robinson, AL. 
Long-term exposure to ambient air pollution and cognitive function in older U.S. adults: The multi-ethnic study of atherosclerosis and air pollution \href{https://ehp.niehs.nih.gov/doi/10.1289/isesisee.2018.P03.1430}{Joint annual meeting: Int'l Society of Exposure Science, Int'l Society for Environmental Epidemiology}, Ottawa, Canada, 26-30 Aug 2018.
\item {\tiny TALK.} Presto, AA; Li, HZ; Robinson, ES; Gu, P; Saha, PK; \textbf{Shah, RU}; Apte, JS; Robinson, AL. Spatial patterns of exposures to nontraditional pollutants: source resolved organic aerosol and ultrafine particles \href{https://ehp.niehs.nih.gov/doi/abs/10.1289/isesisee.2018.S02.03.08}{Joint annual meeting: Int'l Society of Exposure Science, Int'l Society for Environmental Epidemiology}, Ottawa, Canada, 26-30 Aug 2018.
\item {\Large $\star$} {\tiny POSTER.} \textbf{Shah, RU}; Robinson, ES; Gu, P; Presto, AA. Gradients in concentration and composition of fine particulates in a coastal city: downtown dominates a large area emission source in Port of Oakland CA. \href{https://www.healtheffects.org/sites/default/files/AnnualConferenceProgramBook2018_1.pdf}{\textit{Health Effects Institute Annual Conference}}, Chicago IL, 1 May 2018.
\item {\tiny POSTER.} \textbf{Shah, RU}; Florou, K; Presto, AA. Aging atmospheric aerosols on an island in the Mediterranean Sea. \href{http://aaarabstracts.com/2017/viewabstract.php?pid=200}{\textit{American Association for Aerosol Research} conference}, Raleigh NC, 10 Oct 2017.
\item {\tiny POSTER.} \textbf{Shah, RU}; Emamipour, H; Brem, BT; Bond, TC; Rood, MJ.  Hygroscopicity and CCN activity of biomass-burning aerosol. \textit{\href{http://asr.science.energy.gov/meetings/stm/posters/view?id=1325}{US Department of Energy: Atmospheric System Research meeting}}, Vienna VA, Mar 2015.
\end{etaremune}

\newpage
\hrulefill
\textit{\textbf{  Leadership and outreach  }}
\hrulefill
\vspace{-5mm}
\begin{center}
\begin{tabular}{p{0.08\linewidth} p{0.875\linewidth}}
\\[-2ex]
Oct '19 & \begin{flushleft}
\vspace{-6mm} \textbf{Student poster judge}
\newline {\textit{American Association for Aerosol Research Conference}}, Portland OR, 14-19 Oct 2019.
\end{flushleft}
\\[-2ex]
Aug '17 - Jan '19 & \begin{flushleft}
\vspace{-6mm} \textbf{PhD qualifying examination mentor}
\newline Mechanical Engineering Graduate Student Organization \href{https://www.cmumegso.com/}{(MEGSO)}, \textit{CMU}
\end{flushleft}
\\[-2ex]
Jun '15 & \begin{flushleft}
\vspace{-6mm} \textbf{Graduate student instructor}
\newline Girls' Adventures in Mathematics, Engineering and Science \href{http://publish.illinois.edu/womeninengineering/?page_id=297}{(G.A.M.E.S.)} outreach, \textit{UIUC}
\end{flushleft}
\\[-2ex]
Jun '10 - Jun '12 & \begin{flushleft}
\vspace{-6mm} \textbf{Student volunteer}
\newline Poverty alleviation outreach, \href{https://yuvaunstoppable.org/}{\textit{Yuva Unstoppable}}
\end{flushleft}
\end{tabular}
\end{center}
\vspace{-2mm}

\hrulefill
\textit{\textbf{  Awards, honors, and certificates  }}
\hrulefill
\vspace{-2.5mm}
\begin{center}
\begin{tabular}{p{0.07\linewidth} p{0.875\linewidth}}
\\[-2ex]
May '18 & \begin{flushleft}
\vspace{-6mm} \textbf{Student travel award}
\newline Health Effects Institute annual conference, Chicago IL
\end{flushleft}
\\[-2ex]
Mar '17 & \begin{flushleft}
\vspace{-6mm} \textbf{Milton Shaw PhD student travel award}
\newline Mechanical Engineering graduate student research symposium, \textit{CMU}
\end{flushleft}
\\[-2ex]
Mar '15 & \begin{flushleft}
\vspace{-6mm} \textbf{Ivan Racheff student travel grant}
\newline \textit{Civil and Environmental Engineering, UIUC}
\end{flushleft}
\\[-2ex]
Jan '15 & \begin{flushleft}
\vspace{-6mm} \textbf{Certified Associate Developer in LabVIEW software}
\newline \textit{National Instruments, Inc.}
\end{flushleft}
\\[-2ex]
\end{tabular}
\end{center}

\hrulefill
\textit{\textbf{  Peer-reviewer in scientific journals  }}
\hrulefill
\vspace{-3mm}
\begin{multicols}{2}
\begin{itemize}
\item \href{https://www.atmospheric-chemistry-and-physics.net/}{Atmospheric Chemistry and Physics}
\item \href{https://www.journals.elsevier.com/environmental-pollution}{Environmental Pollution}
\item \href{https://www.atmospheric-measurement-techniques.net/}{Atmospheric Measurement Techniques}
\item \href{http://www.aaqr.org/}{Aerosol and Air Quality Research}
\end{itemize}
\end{multicols}
\vspace{1mm}

\hrulefill
\textit{\textbf{  Software skills  }}
\hrulefill
\vspace{-3mm}
\begin{center}
\begin{tabular}{p{0.97\linewidth}}
\\[-2ex]
\href{https://www.wavemetrics.com/products/igorpro}{Igor Pro}
\hfill
\href{http://www.mathworks.com/products/matlab/}{MATLAB}
\hfill
\href{https://www.qgis.org/en/site/about/index.html}{QGIS}
\hfill
\href{https://www.r-project.org/}{R}
\hfill
\href{http://www.latex-project.org/}{\LaTeX}
\hfill
\href{http://www.solidworks.com/}{SOLIDWORKS}
\hfill
\href{http://www.ni.com/labview/}{LabVIEW}
\hfill
\href{https://products.office.com/en-us/home}{MS Office} and \href{https://www.apple.com/iwork/}{iWork}
\end{tabular}
\end{center}
\vspace{1mm}

\hrulefill
\textit{\textbf{  Coursework  }}
\hrulefill
\vspace{-2.5mm}
\begin{multicols}{3}
\begin{itemize}
\item Air Quality Engineering
\item Air Quality Modeling
\item Air Pollutant Sensor Design
\item Air Quality Control
\item Physical Meteorology of the \newline \vspace{-1ex} Atmosphere
\item Fundamental and Advanced Statistical Thermodynamics
\item Advanced Fluid Dynamics
\item Numerical Methods in \newline \vspace{-1ex}Engineering
\item Physical and Chemical \newline \vspace{-1ex}Principles of Envrironmental Engineering
\end{itemize}
\end{multicols}

\hrulefill
\textit{\textbf{  Languages  }}
\hrulefill
\vspace{-2mm}
\begin{center}
\begin{tabular}{p{0.95\linewidth}}
English (proficient)
\hfill
German (intermediate-level)
\hfill
Hindi (proficient)
\hfill
Gujarati (native)
\end{tabular}
\end{center}
\vspace{1mm}
\end{document}
